An Embedding Framework for Consistent Polyhedral Surrogates

### 2021-06-11 poly-embed-journal/poly-embed-journal.tex
Forgot to save

Define the projection $\pi:\reals^\Y\times \reals \to \reals^\Y, (x,c) \mapsto x$.
We can write any face $F_v = \{x \in \reals^\Y \mid \inprod{x}{v} = g(x)\}$.
We claim $\cup_{v \in \V}\pi(F_v) = \reals_+^\Y$.
If there was a $v \in \V$ such that $\pi(F_v) \not \subseteq \reals_+^\Y$, this would imply there is some $x \not \in \reals_+^\Y$ such that $\inprod{x}{v} = c < \infty = g(x)$, contradicting $F_v$ supporting $g$ at $x$.
Thus, $\cup_{v \in \V} \pi(F_v) \subseteq \reals_+^\Y$.
Now for the other direction of subset inclusion, we can take any $x \in \reals_+^\Y$ and show there is some $v \in H'$ such that $\inprod{v}{x} = g(x) < \infty$.
Recall that $\inprod{v}{x} = \infty$ for all $v \in H' \setminus \V$\jessie{nah not true}, but is finite for any $v \in \V$, so we must have $\cup_{v \in \V}\pi(F_v) = \reals_+^\Y$.
Note that we can also take $\theta(v) = F_v \cap \simplex$.
\jessie{I don't like this, but getting out of paralysis}

>>>>

Define the projection $\pi:\reals^\Y\times \reals \to \reals^\Y, (x,c) \mapsto x$.
We can write any face $F_v = \{x \in \reals^\Y \mid \inprod{x}{v} = g(x)\}$.
We claim $\cup_{v \in \V}\pi(F_v) = \reals_+^\Y$.
If there was a $v \in \V$ such that $\pi(F_v) \not \subseteq \reals_+^\Y$, this would imply there is some $x \not \in \reals_+^\Y$ such that $\inprod{x}{v} = c < \infty = g(x)$, contradicting $F_v$ supporting $g$ at $x$.
Thus, $\cup_{v \in \V} \pi(F_v) \subseteq \reals_+^\Y$.
Now for the other direction of subset inclusion, observe that for all $x \in \reals^\Y_+$, we have $g(x) = f(x) = \min_{v \in \V}\inprod{v}{x}$, so there is a $v \in \V$ supporting $g$ at $x$, and therefore $x \in \pi(F_v)$ for some $v \in \V$, and is therefore in the union of projections.
As we have shown both directions of set inclusion, we must have $\cup_{v \in \V}\pi(F_v) = \reals_+^\Y$.
Note that we can also take $\theta(v) = F_v \cap \simplex$.
\jessie{I don't like this, but getting out of paralysis}
